\documentclass{article}
\pagenumbering{gobble}
\usepackage[margin=1in]{geometry}
\usepackage{fontawesome}


\begin{document}

%--------------------------------------- heading  ---------------------------------------
\begin{center}
    \Huge ANDREW FILA
\end{center}
\faEnvelope \hspace{.05in} andrew.m.fila@gmail.com \hspace{.4in} \faPhone \hspace{.05in}(517) 898-3884\hfill \faMapMarker \hspace{.05in} 820 E. Sharon Ave. Houghton, MI, 49931
\rule{\textwidth}{.25mm}

%--------------------------------------- body ---------------------------------------


\begin{quote}
Dear Christina,

    \hspace{2em} I am writing to apply for an introductory role at Burton Industries.


    I am writing to apply for the student linux support technician position listed on Handshake. I am interested in this position because I enjoy working with linux and am looking to gain more experience.
My background in using linux is from personal use, I understand how to work on linux systems and have experience using Fedora, Ubuntu, and Arch distributions. I understand how to work well in a terminal and also have experience in scripting with Bash to automate tasks and create a better workflow.  I would love the opportunity to work in this position and learn more about linux and how it works.
I feel I would be a strong candidate for this position and would like the opportunity to speak with you. I would also be open to discuss any other opportunities you feel would be a good fit.
\\\\
Sincerely,
\\\\
Andrew Fila

\end{quote}






\end{document}
